\documentclass[letterpaper]{article}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{listings}
\usepackage{changepage}
\usepackage{color}
\usepackage{qtree}
\usepackage{fancyvrb}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\title{Homework 3}
\author{Keizou Wang}
\date{February 27, 2025}

\titleformat{\section}{\normalfont\normalsize}{\bfseries\thesection.}{1em}{}
\titleformat{\subsection}{\normalfont\normalsize}{(\textit{\alph{subsection}})}{1em}{}

\lstset{
	language=C++,
	basicstyle={\ttfamily},
	keywordstyle=\color{blue},
	commentstyle=\color{dkgreen},
	stringstyle=\color{mauve},
	tabsize=4,
	showstringspaces=false
}

\begin{document}

\maketitle

\section{Assume that each integer variable occupies four bytes. How much total space is required for
the variables in this code? Justify your answer.}
\begin{adjustwidth}{2.35em}{0pt}
\begin{lstlisting}
{ int a, b, c;
	...
	{ int d, e;
		...
		{ int f;
			...
		}
		...
	}
	...
	{ int g, h, i;
		...
	}
	...
}
\end{lstlisting}
The variables will occupy 24 bytes total because up to 6 variables exist in a given scope at a time.
\end{adjustwidth}

\section{Assuming static scope, what is the referencing environment (i.e., what names are known, and
what do they refer to) at the location marked by (*)?}
\begin{adjustwidth}{2.35em}{0pt}
\begin{Verbatim}[tabsize=4]
procedure P (A,B: real)
	X: real
	procedure Q (B,C: real)
		Y: real
		...
	procedure R (A,C: real)
		Z: real
		... // (*)
	...
\end{Verbatim}
P, Q, R, A, B, C, X, and Z are known. P, Q, R refer to the procedures. B refers to P's parameter. X refers to the variable defined in P. A, C refer to R's parameters. Z refers to the variable defined in R.
\end{adjustwidth}

\end{document}